A Hybrid Ensemble Learning Approach to Star-galaxy Classification

### 2015-04-23 paper/main.tex
update draft.

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage[letterpaper,margin=0.65in]{geometry}
\usepackage[ansinew]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amssymb}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{url}
\usepackage{float}

@@

\label{firstpage}
\begin{abstract}
\textcolor{blue}{
Star-galaxy separation in currently ongoing and future
large photometric surveys, such as DES and LSST,
will detect a vast number of unresolved galaxies at faint magnitudes.
There exist a variety of star-galaxy classification techniques,
each with their own strenths and weaknesses.
In this paper, we present a novel hybrid, ensemble classification
framework that combines and fully exploits different techniques
to produce a more robust classification.
To demonstrate this hybrid technique,
we combine a purely morphological classifier,
a supervised machine learning technique based on random forest,
an unsupervised method based on self-organizing maps,
and a heirarchical Bayeisan template fitting algorithm.
Any of these four methods could
easily be replaced by a similar method
or be extended to include other existing techniques.
Testing with CFHTLenS data,
we demonstrate that our combination technique improves
the overall performance over any individual classification method.
}

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/som_colors.eps}
    \caption{A two-dimensional 10$\times$10 SOM representation
             showing the mean $i$-band magnitude (top left),
             the fraction of true stars in each cell (top right),
             and the mean values of $u-g$ and $g-r$
             for the cross validation data.}
    \label{fig:som_colors}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/weights.eps}
    \caption{A two-dimensional 10$\times$10 SOM representation
             showing the relative weights for the BMC combination technique
             applied to the four individual methods for the CFHTLenS data.}
    \label{fig:weights}
  \end{minipage}
\end{figure*}

@@

We can also use the same SOM to determine the relative weights for 
the four individual classification methods for each cell.
We present the four weight maps for the BMC technique
in Figure~\ref{fig:weights}.
In these maps, a redder color indicates a higher weight,
or equivalently that the corresponding weight performs better in that region.
These weight maps demonstrate the variation in
the performance of the individual techniques across
the two-dimensional parameter space defined by the SOM.
Not surprisingly, the morphological separation
performs best in the top left corner of the $i$-band magnitude map,
which corresponds to the brightest CFHTLenS magnitudes $i \lesssim 20$.
On the other hand, \texttt{TPC} seems to perform best
in the region that corresponds to intermediate magnitudes
$20\gtrsim i \lesssim22.5$ and $1.5<u-g<3.0$.
Our unsupervised learning method \texttt{SOMc}
performs relatively better at fainter magnitudes $i>21.5$
with $0<u-g<0.5$ and $0<g-r<0.5$.
\textcolor{blue}{
Although \texttt{HB} shows the worst performance
when there exists ample training data,
BMC still utilizes information from \texttt{HB}
to produce an overall improvement in performance,
especially at intermediate magnitudes $20\gtrsim i \lesssim22$.
}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag.eps}
  \caption{Purity of morphological separation,
           TPC, and BMC techniques
           as a function of the $i$-band magnitude.
           The top panel shows the histogram of objects in the test data set.
           The second panel shows the fraction of stars
           as a function of magnitude. The error bars are Poisson.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.
           The error bars for completeness and purity are not shown for
           clarity, but they are approximately 10 percent.}
  \label{fig:purity_mag}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_z.eps}
  \caption{The same figures as Figure~\ref{fig:purity_mag},
           but as a function of photometric redshift estimate
           (photo-$z$).}
  \label{fig:purity_z}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_g-r.eps}
  \caption{The same figure as Figure~\ref{purity_mag},
           but as a function of $g-r$ color.}
  \label{fig:purity_g-r}
\end{figure}

\textcolor{blue}{In Figure~\ref{fig:purity_mag}, 
we compare the star and galaxy purity values
for morphological separation, TPC, and BMC techniques
as a function of $i$-band magnitude.
Although morphological separation shows a slightly better performance
at bright magnitudes $i < 21$,
BMC outperforms both morphological separation and TPC
at faint magnitudes $i > 21$.
As shown in Figure.~\ref{fig:purity_mag},
the histogram of distribution of objects peaks at $i \sim 22$,
and BMC therefore outperforms the morphological separation technique
for the majority of objects.
It is also clear that BMC outperforms TPC over all magnitudes.
BMC can presumably accomplish this by combining information from
all base classifiers,
\eg giving more weight to the morphological separation method
at bright magnitudes.}

\textcolor{blue}{We also show the star and galaxy purity values
of Table~\ref{table:metrics_all} as a function of
photometric redshift in Figure~\ref{fig:purity_z}.
Photo-$z$ is estimated with
the \texttt{BPZ} algorithm~\citep{benitez2000bayesian}
and provided with
the CFHTLenS photometric redshift catalogue~\citep{Hildebrandt2012}.
Although the morphological separation method outperformed BMC
at bright magnitudes in Figure.~\ref{fig:purity_mag},
it is clear that BMC outperforms
both morphological separation and TPC over all redshift range.}

\textcolor{blue}{In Figure.~\ref{fig:purity_g-r},
we present how the star and galaxy purity values vary
as a function of $g-r$ color.
It is again clear that BMC outperforms
both morphological separation and TPC over all $g-r$ color range.  }

@@

It is very costly in terms of telescope time to
obtain a large sample spectroscopic observations
down to the limiting magnitude of a photometric sample.
Thus, we investigate the impact of training set quality
by analyzing in detail a more realistic case
where the training data is available
only for a small number of objects at bright magnitudes.
To emulate this scenario,
we only use objects that have spectroscopic labels
from the VVDS 0226-04 field (which is located within the CFHTLS W1 field)
and impose a magnitude cut of $i < 22.0$ in the training data,
leaving us a training set with 1,365 objects.
We apply the same four star-galaxy classification techniques
and four different combination methods,
and test them on the same test data.
Since the demographics of sources in the test data set
does not show the same distribution as the training data set,
this also serves as a test of the efficacy of heterogenous training data.

@@

Without sufficient training data,
the advantage of classification combination techniques
is more obvious.
Even WA, the simplest of combination techniques, outperforms
all individual classification techniques.
Interestingly, although TPC does not perform better
than morphological separation,
BoM still chooses TPC as the best model within each SOM cell
and shows exactly the same performance metrics as TPC.
Stacking and BMC techniques still outperform
all individual classification techniques,
and BMC's improvement in performance over TPC or mophological separation
is impressive.
Overall, the improvements are small but still significant
since these metrics are averaged over the full test data.

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/som_colors_cut.eps}
    \caption{The same figure as Figure~\ref{fig:som_colors}
        but for the BMC technique applied to the four individual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:som_colors_cut}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/weights_cut.eps}
    \caption{The same figure as Figure~\ref{fig:weights}
        but for the BMC technique applied to the four invidiual methods
        trained with the CFHTLenS data in the VVDS W1 field
        with $i < 22$.}
    \label{fig:weights_cut}
  \end{minipage}
\end{figure*}

In Figure~\ref{fig:weights_cut}, we again show the $10\times10$
two-dimensional weight map defined by the SOM.
%It seems that \texttt{TPC} performs well
%in most of the parameter space.
\textcolor{blue}{When the quality of training data is relatively poor,
the performance of data driven algorithms will decrease,
while the performance of template fitting algorithms such as \texttt{HB}
is independent of training data.
Thus, comparing the weight maps of Figure~\ref{fig:weights}
and Figure~\ref{fig:weights_cut},
it is perhaps not surprising that
BMC algorithm now uses more information from
morphological separation and \texttt{HB},
while it uses considerably less information from TPC.
%Another interesting pattern is that
%\texttt{SOMc} and morphological separation seem complementary;
%\texttt{SOMc} is weighted most strongly at fainter magnitudes,
%while the morphological separation method
%is weighted most strongly at brighter magnitudes.
It is not surprising that the morphological separation method
performs best at bright magnitudes,
and BMC assigns more weight to \texttt{HB} at fainter magnitudes.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag_cut.eps}
  \caption{Purity as a function of the $i$-band magnitude
           for morphological separation, TPC, and BMC techniques
           in the VVDS W1 field with $i < 22$.
           We repat in the top panel shows the histogram of objects
           in the test data set.
           The second panel shows the fraction of stars
           in the VVDS W1 and W4 fields.
           The error bars are Poisson.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.
           The error bars for completeness and purity are not shown for
           clarity, but they are approximately 10 percent.}
  \label{fig:purity_mag_cut}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_z_cut.eps}
  \caption{The same figures as Figure~\ref{fig:purity_mag_cut},
           but as a function of photo-$z$.}
  \label{fig:purity_z_cut}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_g-r_cut.eps}
  \caption{The same figure as Figure~\ref{purity_mag_cut},
           but as a function of $g-r$ color.}
  \label{fig:purity_g-r_cut}
\end{figure}

We present the star and galaxy purity values
of Table~\ref{table:metrics_vvds} as a function of
$i$-band magnitude in Figure~\ref{fig:purity_mag_cut}.
It is clear that BMC outperforms both
morphological separation and TPC classification techniques
over all magnitudes.
The galaxy purity of BMC is significantly better
than that of TPC at bright magnitudes, $i\lesssim21.5$,
while they are similar at faint magnitudes.
The star purity of BMC shows improvement over that of TPC
at faint magnitudes,
while they are similar at bright magnitudes.
As suggested by the weight maps in Figure~\ref{fig:weights_cut},
BMC can accomplish this by combining information from
all base classifiers,
\eg giving more weight to the morphological separation method
at bright magnitudes.
We can also see in the bottom two panels that
the performance of morphological separation suffers
at intermediate magnitudes $21\lesssim i \lesssim23$,
while BMC shows consistently better performance
over all magnitude ranges.

We also show the star and galaxy purity values
of Table~\ref{table:metrics_vvds} as a function of
photometric redshift in Figure~\ref{fig:purity_z}.
Photo-$z$ is estimated with
the \texttt{BPZ} algorithm~\citep{benitez2000bayesian}
and provided with
the CFHTLenS photometric redshift catalogue~\citep{Hildebrandt2012}.
It is again clear that BMC outperforms
both individual classification techniques over all redshift range.

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/p_dist_all.eps}
    \caption{Histogram of the posterior probability that
             a source is a star for morphological separation (top),
             TPC (middle), and BMC (bottom) techniques
             for the entire training data
             (the CFHTLenS data in the DEEP2, SDSS, VIPERS, and VVDS
             fields as discussed in Section~\ref{section:rich_training}).}
    \label{fig:p_dist_all}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/p_dist_cut.eps}
    \caption{The same figures as Figure~\ref{fig:p_dist_all},
             but for TPC and BMC trained with 
             poor training data
             (the CFHTLenS data in the VDDS field
             with a magnitude cut of $i<22$).}
    \label{fig:p_dist_cut}
  \end{minipage}
\end{figure*}

We show the distribution of posterior star probabilities
in Figures~\ref{fig:p_dist_all} and \ref{fig:p_dist_cut}.
The histogram of spectroscopic galaxies is in blue,
and the histogram of true stars is in red.
It is interesting that the BMC technique assigns
a probability $P\left(S\right)$ greater than 0.6
to almost no true galaxies in Figure~\ref{fig:p_dist_all},
presumably because BMC utilizes information from
different types of classification techniques.
This pattern is more pronounced in Figure~\ref{fig:p_dist_cut},
where the $P\left(S\right)$ distribution of BMC for true galaxies
falls off sharply at $P\left(S\right)\approx0.95$,
while morphological separation and TPC techniques
classify some true galaxies as stars with absolute certainty.

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figures/color_color.eps}
  \caption{Color-color diagrams of sources with
           $0.45<P\left(S\right)<0.55$ when the BMC technique
           is applied to the poor training data.}
  \label{fig:color_color}
\end{figure*}

To identify the regions in color-color space
where our BMC technique struggles to classify stars and galaxies,
we present the distribution over the color-color space for sources with
$0.45 < P(S) < 0.55$ in Figure~\ref{fig:color_color}.
Not surprisingly, these regions correspond to
where there is a significant overlap between stars and galaxies
in the color space.
It may be possible to improve the performance of
star-galaxy classification by obtaining more information
through spectroscopic follow-up, manual study, or citizen science projects,
or by developing a classification technique specifically designed
for these regions of the color space and
combining it with other techniques in a Bayesian framework.

@@

It is very costly in terms of telescope time to
obtain a large sample spectroscopic observations
down to the limiting magnitude of a photometric sample.
Thus, we investigate the impact of training set quality
by imposing various magnitude and $z$ cuts
to decrease the size of the training set.

In Figure.~\ref{fig:perform_mag_cut}, we present
a visual comparison between different classification techniques
when various magnitude cuts are applied.

In Figure.~\ref{fig:perform_z_cut}, we also present
the result of imposing various $z$ cuts.

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/perform_mag_cut.eps}
    \caption{The classification performance metrics for TPC, HB, morphology,
      and BMC as applied to the CFHTLenS data in the VVDS field
      with various magnitude cuts.
      The top panel shows the number of sources in the training set
      at corresponding magnitude cuts.
      We show only one of the four combination methods, BMC,
      which has the best overall performance.}
    \label{fig:perform_mag_cut}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \includegraphics[width=\textwidth]{figures/perform_z_cut.eps}
    \caption{Same as Figure.~\ref{fig:perform_mag_cut} using
      $z_{\text{spec}}$ cuts.}
    \label{fig:perform_z_cut}
  \end{minipage}
\end{figure*}
\section{Conclusions}
  \label{section:conclusions}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage[letterpaper,margin=0.65in]{geometry}
\usepackage[ansinew]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amssymb}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{url}
\usepackage{placeins}

@@

\label{firstpage}
\begin{abstract}
\textcolor{blue}{
Star-galaxy separation in currently ongoing and future
large photometric surveys, such as DES and LSST,
will detect a vast number of unresolved galaxies at faint magnitudes.
There exist a variety of star-galaxy classification techniques,
each with their own strenths and weaknesses.
In this paper, we present a novel hybrid, ensemble classification
framework that combines and fully exploits different techniques
to produce a more robust classification.
To demonstrate this hybrid technique,
we combine a purely morphological classifier,
a supervised machine learning technique based on random forest,
an unsupervised method based on self-organizing maps,
and a heirarchical Bayeisan template fitting algorithm.
Any of these four methods could
easily be replaced by a similar method
or be extended to include other existing techniques.
Testing with CFHTLenS data,
we demonstrate that our combination technique improves
the overall performance over any individual classification method.}

\textcolor{red}{more abstract.}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/som_colors.eps}
  \caption{A two-dimensional 10$\times$10 SOM representation
           showing the mean $i$-band magnitude (top left),
           the fraction of true stars in each cell (top right),
           and the mean values of $u-g$ and $g-r$
           for the cross validation data.}
  \label{fig:som_colors}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/weights.eps}
  \caption{A two-dimensional 10$\times$10 SOM representation
           showing the relative weights for the BMC combination technique
           applied to the four individual methods for the CFHTLenS data.}
  \label{fig:weights}
\end{figure}

@@

We can also use the same SOM to determine the relative weights for 
the four individual classification methods for each cell.
We present the four weight maps for the BMC technique
in Figure~\ref{fig:weights}.
In these maps, a redder color indicates a higher weight,
or equivalently that the corresponding weight performs better in that region.
These weight maps demonstrate the variation in
the performance of the individual techniques across
the two-dimensional parameter space defined by the SOM.
Not surprisingly, the morphological separation
performs best in the top left corner of the $i$-band magnitude map,
which corresponds to the brightest CFHTLenS magnitudes $i \lesssim 20$.
On the other hand, \texttt{TPC} seems to perform best
in the region that corresponds to intermediate magnitudes
$20\gtrsim i \lesssim22.5$ and $1.5<u-g<3.0$.
Our unsupervised learning method \texttt{SOMc}
performs relatively better at fainter magnitudes $i>21.5$
with $0<u-g<0.5$ and $0<g-r<0.5$.
\textcolor{blue}{
Although \texttt{HB} shows the worst performance
when there exists ample training data,
BMC still utilizes information from \texttt{HB}
to produce an overall improvement in performance,
especially at intermediate magnitudes $20\gtrsim i \lesssim22$.
Another interesting pattern is that
the four techniques seem complementary,
and they are weighted most strongly in different regions
of the SOM representations.}

\textcolor{blue}{In Figure~\ref{fig:purity_mag}, 
we compare the star and galaxy purity values
for morphological separation, TPC, and BMC techniques
as a function of $i$-band magnitude for the differential counts.
We use the kernel density estimation \cite[KDE;][]{silverman1986density}.
Although morphological separation shows a slightly better performance
at bright magnitudes $i < 21$,
BMC outperforms both morphological separation and TPC
at faint magnitudes $i > 21$.
As the top panel shows,
the number count distribution peaks at $i \sim 22$,
and BMC therefore outperforms the morphological separation technique
for the majority of objects.
It is also clear that BMC outperforms TPC over all magnitudes.
BMC can presumably accomplish this by combining information from
all base classifiers,
\eg giving more weight to the morphological separation method
at bright magnitudes.
In Figure~\ref{fig:purity_mag_itnegrated}, we show
the overall galaxy and star purity as a function of magnitude
for the integrated counts.
BMC is able to maintain a galaxy purity of 0.980
up to $i \sim 24.5$, while the galaxy purity of
the morphological separation method drops to 95.7\%
beyond $i \lesssim 21$.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag.pdf}
  \caption{Purity as a function of the $i$-band magnitude
           as estimated by the kernel density estimation (KDE) method
           for the differential counts.
           The top panel shows the histogram with a bin size of 0.1 mag
           and the KDE for objects in the test set.
           The second panel shows the fraction of stars estimated by KDE
           as a function of magnitude.
           The bottom two panels compare
           the galaxy and star purity for BMC, TPC, and 
           morphological separation as a function of magnitude.
           Results for BMC, TPC, and morphological separation are in
           red, green, and blue, respectively.
           The $1 \sigma$ confidence bands are estaimted by
           bootstrap resampling.}
  \label{fig:purity_mag}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag_integrated.pdf}
  \caption{Purity as a function of the $i$-band magnitude
           for the integrated counts.
           The bottom two panels compare
           the galaxy and star purity for BMC, TPC, and 
           morphological separation as a function of magnitude.
           Results for BMC, TPC, and morphological separation are in
           red, green, and blue, respectively.
           The $1 \sigma$ error bars are Poisson.}
  \label{fig:purity_mag_integrated}
\end{figure}

\textcolor{blue}{We also show the star and galaxy purity values
of Table~\ref{table:metrics_all} as a function of
photometric redshift in Figure~\ref{fig:purity_z}.
Photo-$z$ is estimated with
the \texttt{BPZ} algorithm~\citep{benitez2000bayesian}
and provided with
the CFHTLenS photometric redshift catalogue~\citep{Hildebrandt2012}.
The advantage of BMC over morphological separation and TPC is
now more pronounced in Figure~\ref{fig:purity_z}.
Although the morphological separation method outperformed BMC
at bright magnitudes in Figure.~\ref{fig:purity_mag},
it is clear that BMC outperforms
both morphological separation and TPC over all redshift range.
We also present in Figure.~\ref{fig:purity_g-r}
how the star and galaxy purity values vary
as a function of $g-r$ color.
It is again clear that BMC outperforms
both morphological separation and TPC over all $g-r$ color range.  }

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_z.pdf}
  \caption{The same figures as Figure~\ref{fig:purity_mag},
           but as a function of photometric redshift estimate
           (photo-$z$).
           The bin size of histogram in the top panel is 0.02.}
  \label{fig:purity_z}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_g-r.pdf}
  \caption{The same figure as Figure~\ref{purity_mag},
           but as a function of $g-r$ color.
           The bin size of histogram in the top panel is 0.05.}
  \label{fig:purity_g-r}
\end{figure}

\textcolor{blue}{We show the distribution of posterior star probabilities
in Figures~\ref{fig:p_dist}.
The histogram of spectroscopic galaxies is in red,
and the histogram of true stars is in black.
It is interesting that the BMC technique assigns
a probability $P\left(S\right)$ greater than 0.75
to significally fewer true galaxies than TPC,
presumably because BMC utilizes information from
different types of classification techniques.}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/p_dist.pdf}
  \caption{Histogram of the posterior probability that
           a source is a star for morphological separation (top),
           TPC (middle), and BMC (bottom) techniques
           for a high-quality training data.
           The bin size is 0.05.}
  \label{fig:p_dist_all}
\end{figure}

@@

It is very costly in terms of telescope time to
obtain a large sample spectroscopic observations
down to the limiting magnitude of a photometric sample.
Thus, we investigate the impact of training set quality
by considering a more realistic case
where the training data is available
only for a small number of objects with bright magnitudes.
\textcolor{blue}{ To emulate this scenario,
we only use objects that have spectroscopic labels
from the VVDS 0226-04 field (which is located within the CFHTLS W1 field)
and impose a magnitude cut of $i < 22.0$ in the training data,
leaving us a training set with 1,365 objects.
We apply the same four star-galaxy classification techniques
and four different combination methods,
and test them on the same test data.
Since the demographics of sources in the test data set
are different from the distribution of the training data set,
this also serves as a test of the efficacy of heterogenous training data.}

@@

Without sufficient training data,
the advantage of classification combination techniques
is more obvious.
Even WA, the simplest of combination techniques, outperforms
all individual classification techniques.
Interestingly, although TPC does not perform better
than morphological separation,
BoM still chooses TPC as the best model within each SOM cell
and shows exactly the same performance metrics as TPC.
Stacking and BMC techniques still outperform
all individual classification techniques,
and BMC's improvement in performance over TPC or mophological separation
is impressive.
Overall, the improvements are small but still significant
since these metrics are averaged over the full test data.
\textcolor{red}{Note: Numbers for WA, BOM, and Stacking seem a little bit off.
Will investigate.}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/som_colors_cut.eps}
  \caption{The same figure as Figure~\ref{fig:som_colors}
      but for the BMC technique applied to the four individual methods
      trained with the CFHTLenS data in the VVDS W1 field
      with $i < 22$.}
  \label{fig:som_colors_cut}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/weights_cut.eps}
  \caption{The same figure as Figure~\ref{fig:weights}
      but for the BMC technique applied to the four invidiual methods
      trained with the CFHTLenS data in the VVDS W1 field
      with $i < 22$.}
  \label{fig:weights_cut}
\end{figure}

In Figure~\ref{fig:weights_cut}, we again show the $10\times10$
two-dimensional weight map defined by the SOM.
%It seems that \texttt{TPC} performs well
%in most of the parameter space.
\textcolor{blue}{When the quality of training data is relatively poor,
the performance of data driven algorithms will decrease,
while the performance of template fitting algorithms such as \texttt{HB}
is independent of training data.
Thus, when the weight maps of Figure~\ref{fig:weights}
and Figure~\ref{fig:weights_cut} are compared,
it is clear that
BMC algorithm now uses more information from
morphological separation and \texttt{HB},
while it uses considerably less information from the 
data-driven methods, \texttt{TPC} and \texttt{SOMc}.
Not surprisingly, the morphological separation method
performs best at bright magnitudes,
and BMC assigns more weight to \texttt{HB} at fainter magnitudes.}

\textcolor{blue}{We present the star and galaxy purity values as a function of
$i$-band magnitude for the differential counts
in Figure~\ref{fig:purity_mag_cut}.
Compred to Figure~\ref{fig:purity_mag},
the purity of data-driven technique, TPC, suffers a significant
decrease in purity.
However, the purity of BMC does not show such a significant drop
and decreases by only 2-5\%, and BMC still outperforms
the morphological separation method at fainter magnitudes $i > 21$.
while they are similar at bright magnitudes.
As suggested by the weight maps in Figure~\ref{fig:weights_cut},
BMC can accomplish this by shifting the weights assigned to
each base classifier in different SOM cells,
\ie assigning less weight to \texttt{TPC}
and more weight to \texttt{HB} and morphological separation
when the quality of training data is relatively poor.
We can also see in the bottom two panels that
the performance of morphological separation suffers
at fainter magnitudes $i > 21$,
while BMC shows consistently better performance over all magnitude ranges.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag_cut.pdf}
  \caption{Purity as a function of the $i$-band magnitude
           for morphological separation, TPC, and BMC techniques
           in the VVDS W1 field with $i < 22$.
           Top panel shows the histogram and KDE for number distribution
           in the test data set.
           The second panel shows the fraction of stars
           in the VVDS W1 and W4 fields in green and blue, respectively.
           The bottom two panels compare
           the galaxy and star purity for morphological separation, TPC,
           and BMC techniques as a function of magnitude.}
  \label{fig:purity_mag_cut}
\end{figure}

\textcolor{blue}{In Figure~\ref{fig:purity_mag_cut_itnegrated}, we show
the overall galaxy and star purity as a function of magnitude
for the integrated counts.
Even when \texttt{TPC} and \texttt{SOMc} are trained on heterogenous data,
BMC is able to maintain a galaxy purity of 0.970
up to $i \sim 24.5$, and it sill outperforms morphological separation
at fainter magnitudes $i \gtrsim 21$.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_mag_cut_integrated.pdf}
  \caption{Purity as a function of the $i$-band magnitude
           for the integrated counts.
           The bottom two panels compare
           the galaxy and star purity for BMC, TPC, and 
           morphological separation as a function of magnitude.
           Results for BMC, TPC, and morphological separation are in
           red, green, and blue, respectively.
           The error bars are Poisson.}
  \label{fig:purity_mag_cut_integrated}
\end{figure}

We also show the star and galaxy purity values
as a function of
photometric redshift in Figure~\ref{fig:purity_z_cut},
and as a function of $g-r$ in Figure~\ref{fig:purity_g_r_cut}.
Compared to Figure~\ref{fig:purity_z} and \ref{fig:purity_g_r},
where \texttt{TPC} and \texttt{SOMc} were trained
on a high-quality training data,
the performance of BMC is worse in some photo-$z$ and $g-r$ ranges.
However, this drop in performance seems to be confined to
only a small number of objects in particular parameter ranges,
and BMC still outperforms both \texttt{TPC} and morphological separation
for the majority of objects.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_z_cut.pdf}
  \caption{The same figures as Figure~\ref{fig:purity_mag_cut},
           but as a function of photo-$z$.}
  \label{fig:purity_z_cut}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/purity_g_r_cut.pdf}
  \caption{The same figure as Figure~\ref{purity_mag_cut},
           but as a function of $g-r$ color.}
  \label{fig:purity_g-r_cut}
\end{figure}

The difference between the posterior probability distribution of
TPC and that of BMC is now more pronounced in Figure~\ref{fig:p_dist_cut},
where the $P\left(S\right)$ distribution of BMC for true galaxies
falls off sharply at $P\left(S\right)\approx0.95$,
while morphological separation and TPC techniques
classify some true galaxies as stars with absolute certainty.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/p_dist_cut.pdf}
  \caption{The same figures as Figure~\ref{fig:p_dist_all},
           but for TPC and BMC trained with 
           poor training data
           (the CFHTLenS data in the VDDS field
           with a magnitude cut of $i<22$).}
  \label{fig:p_dist_cut}
\end{figure}

%\begin{figure*}
%  \centering
%  \includegraphics[width=\linewidth]{figures/color_color.eps}
%  \caption{Color-color diagrams of sources with
%           $0.45<P\left(S\right)<0.55$ when the BMC technique
%           is applied to the poor training data.}
%  \label{fig:color_color}
%\end{figure*}
%
%To identify the regions in color-color space
%where our BMC technique struggles to classify stars and galaxies,
%we present the distribution over the color-color space for sources with
%$0.45 < P(S) < 0.55$ in Figure~\ref{fig:color_color}.
%Not surprisingly, these regions correspond to
%where there is a significant overlap between stars and galaxies
%in the color space.
%It may be possible to improve the performance of
%star-galaxy classification by obtaining more information
%through spectroscopic follow-up, manual study, or citizen science projects,
%or by developing a classification technique specifically designed
%for these regions of the color space and
%combining it with other techniques in a Bayesian framework.

@@

\textcolor{blue}{The BMC technique we have demonstrated in this work uses
two training based algorithms as base classifiers.
Ideally, the training data should mirror the entire parameter space
occupied the data to be classified.
Yet we have seen that the BMC technique do reliably
extraplotate past the limits of the training data,
even when some base classifiers are trained on a hetorogenous data
with a magnitude cut imposed.
In this section, we further investigate
if and where BMC begins to break down
by imposing various magnitude, photo-$z$, and color cuts
to decrease the size of the training set.}

\textcolor{blue}{In Figure.~\ref{fig:perform_mag_cut}, we present
a visual comparison between different classification techniques
when various magnitude cuts are applied in the training data
and the performance is measured on the same test set.
The top panel shows that the size of training set
decreases as we impose more restrictive magnitude cut.
It is remarkable that BMC is able to reliably extrapolate
past the training data and outperform \texttt{HB}, \texttt{TPC},
and morphological separation in all performance metrics,
even the demographics of training set does not accurately sample 
the data to be classified and the size of training set is decreased.
The performance is consistent until we impose a magnitude cut
of $i < 20.5$ on the training data,
beyond which point BMC finally performs worse than morphological separation.}

\textcolor{blue}{Similarly, we also present impose various
spectroscopic redshfit and color cuts in the training data
in Figure~\ref{fig:perform_z_cut} and Figure~\ref{fig:perform_g_r_cut},
resepctively.
The area under the ROC curve measures the global performance,
and BMC still outperforms \texttt{HB} and \texttt{TPC} globally in both cases,
even when a very restrictive cuts are applied on the training set.
Locally, BMC begins to perform worse than morphological separation
when a conservative cut of $z_{\mathrm{spec}} < 0.6$ is imposed.
A color cut seems to have more pronounced effect in the performance of BMC
as shown in Figure~\ref{fig:perform_g_r_cut}.
When the training data set is restricted to $g - r > 0.4$,
BMC performs worse than morphological separation.}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/perform_mag_cut.eps}
    \caption{The classification performance metrics for TPC, HB, morphology,
      and BMC as applied to the CFHTLenS data in the VVDS field
      with various magnitude cuts.
      The top panel shows the number of sources in the training set
      at corresponding magnitude cuts.
      We show only one of the four combination methods, BMC,
      which has the best overall performance.}
    \label{fig:perform_mag_cut}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/perform_z_cut.eps}
    \caption{Same as Figure.~\ref{fig:perform_mag_cut} using
      $z_{\text{spec}}$ cuts.}
    \label{fig:perform_z_cut}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figures/perform_g_r.eps}
    \caption{Same as Figure.~\ref{fig:perform_mag_cut} using
      $g - r$ color cuts.}
    \label{fig:perform_g_r_cut}
\end{figure}

\section{Conclusions}
  \label{section:conclusions}
